\mpx{}: Mixed Precision Training for JAX

### 2025-07-03 docs/paper/main.tex
major refactoring of docs and namespaces

@@

The \mpx{} library offers essential transformations for mixed precision training while preserving JAX's low-level flexibility. 
Similar to JMP~\citep{jmp}, implementationts design leverages JAX's type-promotion behavior\footnote{\url{https://docs.jax.dev/en/latest/jep/9407-type-promotion.html}}, ensuring that operations are executed in the precision to which inputs and outputs have been cast—provided all constants in the function are positioned on the left side of the type-promotion lattice. 
Consequently, \mpx{} primarily focuses on casting function inputs and outputs to the desired precision.

@@

The desktop PC trains the ViT on CIFAR100 while the high-performance cluster handles ImageNet1k, dividing each batch equally across GPUs using a data-parallel approach. We train without gradient accumulation, which could further optimize runtime and memory consumption

@@

>>>>

% # build: python3 -m build --sdist
% # upload: twine upload --repository pypi dist/*

@@

The \mpx{} library offers essential transformations for mixed precision training while preserving JAX's low-level flexibility. 
Similar to JMP~\citep{jmp}, our implementation's design leverages JAX's type-promotion behavior\footnote{\url{https://docs.jax.dev/en/latest/jep/9407-type-promotion.html}}, ensuring that operations are executed in the precision to which inputs and outputs have been cast—provided all constants in the function are positioned on the left side of the type-promotion lattice. 
Consequently, \mpx{} primarily focuses on casting function inputs and outputs to the desired precision.

@@

The desktop PC trains the ViT on CIFAR100 while the high-performance cluster handles ImageNet1k, dividing each batch equally across GPUs using a data-parallel approach. We train without gradient accumulation, which could further optimize runtime and memory consumption.

@@

We thank Lukas Wildberger for helpful discussions and suggestions.
